6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-21 paper.tex
Relate and provide evidence for eval

\begin{minted}[fontfamily=fi4]{yaml}
  host: "example-production-1"
  service: "example-service"
  component: "nginx"
  description: "Error: Process nginx not listening on port 80"
  state: "error"
  metric: 0
  type: "component"
  tags: ['check']
  notify_endpoint: "/example-service/components/nginx"
  ttl: 15
\end{minted}

@@

\pagebreak
\subsection{Email and SMS Notifications}

@@

\begin{center}
  \includegraphics[scale=0.28]{web-ui/service-overview.png}
\end{center}

@@

\begin{center}
  \includegraphics[scale=0.33]{web-ui/architecture.png}
\end{center}

@@

\begin{center}
  \includegraphics[scale=0.28]{web-ui/incidents.png}
\end{center}

@@

\begin{center}
  \includegraphics[scale=0.28]{web-ui/events.png}
\end{center}

@@

\pagebreak
\section{Deployment \& Provisioning}

@@

        Three production systems were described using the service specification DSL, they could all be represented appropriately.

@@

        Service specifications, such as the examples satisfying the previous requirement, can be executed using the `check' and `start' commands. When using the check command, output is similar to that seen in \ref{}.

        The service overview page displays the results of checks on started daemons \ref{}.

@@

        The service discovery functionality was implemented and tested on a Linux virtual machine, it correctly identified the components specified in the component definitions file. Clearly, this functionality will not work with previously un-documented services.

@@

        The example service specification shows the usage of the tool with an external RubyGem to interface with Redis, assertions can be made on the results using the built in methods and standard Ruby functionality as demonstrated. This pattern can be followed with any external RubyGem.

@@

        The management agent reports its check results back to the streaming event service according to the schema specified in~\ref{EventSchema}. The results of this can be verified by observing that the correct success/failure messages and description are displayed on the Web UI.

@@

        The web interface effectively presents the state of the system, including all of the above details. Screenshots of this functionality can be found in \ref{}

@@

        The web interface effectively presents the results of health checks, including specific error messages to aid debugging efforts. Screenshots of this functionality can be found in \ref{}

@@

        The management API tracks a number of different event types, including: `deployment', `configuration', `host-registration', `host-deregistration', `check-result'. The web interface presents these events in chronological order as seen in \ref{}.

@@

        The management API uses event and incident data to calculate ``Mean Time Between Failure (MBTF)", ``Mean Time Before Recovery (MTBR)" and the derived ``Service Availability". The web interface presents these events in chronological order as seen in \ref{}.

@@

        As displayed in \ref{}, the tool sends emails when incidents are triggered and resolved.

@@

        As displayed in \ref{}, the tool sends SMS messages when incidents are triggered and resolved.

@@

        The Ansible playbooks discussed in \ref{}, together with the Packer build process explained in the same section make this possible. Example build artifacts are linked in \ref{}.

@@

        \ref{}

@@

% \chapter{Appendices}

\printbibliography[title=References]
% \include{appendix}

>>>>

\label{eventschema}
\begin{minted}[fontfamily=fi4]{yaml}
  host: "example-production-1"
  service: "example-service"
  component: "nginx"
  description: "Error: Process nginx not listening on port 80"
  state: "error"
  metric: 0
  type: "component"
  tags: ['check']
  notify_endpoint: "/example-service/components/nginx"
  ttl: 15
\end{minted}

@@

\pagebreak
\subsection{Email and SMS Notifications}
\label{notifications}

@@

\begin{center}
  \label{webui-overview}
  \includegraphics[scale=0.28]{web-ui/service-overview.png}
\end{center}

@@

\begin{center}
  \label{webui-architecture}
  \includegraphics[scale=0.33]{web-ui/architecture.png}
\end{center}

@@

\begin{center}
  \label{webui-incidents}
  \includegraphics[scale=0.28]{web-ui/incidents.png}
\end{center}

@@

\begin{center}
  \label{webui-events}
  \includegraphics[scale=0.28]{web-ui/events.png}
\end{center}

@@

\pagebreak
\section{Deployment \& Provisioning}
\label{ansible}

@@

        A number of production systems were described using the service specification DSL, all components could be represented accurately and concisely, examples can be found in \autoref{dslexamples}.

@@

        Service specifications, such as the examples satisfying the previous requirement, can be executed using the `check' and `start' commands.

@@

        The service discovery functionality was implemented and tested on a Linux virtual machine, it correctly identified the components specified in the component definitions file. Detection is limited to a small set of service definitions, currently.

@@

        The example service specification in \autoref{dslgem} shows the usage of the tool with an external RubyGem to interface with Redis, assertions can be made on the results using the built in methods and standard Ruby functionality as demonstrated. This pattern can be followed with any external RubyGem.

@@

        The management agent reports its check results back to the streaming event service according to the schema specified in \autoref{eventschema}. The results of this can be verified by observing that the correct success/failure messages and description are displayed on the Web UI.

@@

      The web interface effectively presents the state of the system, including all of the above details. Screenshots of this functionality can be found in \autoref{webui-overview} and \autoref{webui-architecture}

@@

      The web interface effectively presents the results of health checks, including specific error messages to aid debugging efforts. Evidence of this functionality is provided in \autoref{webui-overview}.

@@

        The management API tracks a number of different event types, including: `deployment', `configuration', `host-registration', `host-deregistration', `check-result'. The web interface presents these events in chronological order as seen in \autoref{webui-events}.

@@

        The management API uses event and incident data to calculate ``Mean Time Between Failure (MBTF)", ``Mean Time Before Recovery (MTBR)" and the derived ``Service Availability". The web interface presents these events in chronological order as seen in \autoref{webui-incidents}.

@@

        As displayed in \autoref{notifications}, the tool sends emails when incidents are triggered and resolved.

@@

        As displayed in \autoref{notifications}, the tool sends SMS messages when incidents are triggered and resolved.

@@

        The Ansible playbooks discussed in \autoref{ansible}, together with the Packer build process explained in the same section make this possible.

@@

        As discussed in previous sections, all data transmission between the management API and the system under test is protected by SSL encryption.

@@

\printbibliography[title=References]

\pagebreak
\section{Appendix}
\subsection{Service Specification Examples}
\label{dslexamples}

\subsubsection{X-Time}
\label{dslgem}
\inputminted[fontfamily=fi4]{ruby}{appendices/x-time.rb}

\subsubsection{X-Awards Site}
\inputminted[fontfamily=fi4]{ruby}{appendices/x-awards-site.rb}

\subsubsection{Workspace +}
\inputminted[fontfamily=fi4]{ruby}{appendices/workspace.rb}
